---
title: "Estudio Demografico estudiantes Graduados UPR"
author: "Sofía Meléndez Cartagena"
date: "6/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
```

```{r, include=FALSE}
Datum <- read_csv(file = "../Data/Graduados 2020, info (Respuestas).csv")
```

## Disclousure

The people who took this survey are in their mayority spanish speakers. So the questions and answers will be in spanish. A translation can be made available if there is interest.

## Global concerns

As part of the survey, the final quesiton involved writing in concerns. These are all of them:

```{r, echo=FALSE}
 Wor<-Datum %>%
  filter(`¿Tiene alguna preocupación que entiende debe ser traída a alguna reunion con la administacion?`!= is.na(`¿Tiene alguna preocupación que entiende debe ser traída a alguna reunion con la administacion?`)) %>%
  select(`¿Tiene alguna preocupación que entiende debe ser traída a alguna reunion con la administacion?`)

Wor
```

Most of the students express that they feel like they should be included in school legislations that involve their livelyhood. The are worried about the lack of comunication and that the aproval of this certification will make it imposible for them to study. They also express that in later years the renumeration for work done has taken months to be given and that this will be repeated once again this year.

```{r, include=FALSE}
write_tsv(Wor, "../Document/Student_concerns.tsv")
```

## Answers to the questions

Before telling a story, I want to make clear what is it exacltly that we have here.I won't ilustrate 100% of the questions as they will clutter the document. But they are available in the data set for analysis. 

```{r, echo=FALSE}
ggplot(Datum, aes(x = `¿Cursa Maestría o Doctorado?`))+
  geom_bar()
#ggsave("../Graphs/MoD.png")
```

```{r, echo=FALSE}
ggplot(Datum, aes(x = `¿Que año cursa?`)) +
  geom_bar()

#ggsave("../Graphs/Year.png")
```

```{r, echo=FALSE}
ggplot(Datum, aes(x = `Usted es ...`))+
  geom_bar()
#ggsave("../Graphs/LocOint.png")
```

```{r, echo=FALSE}
ggplot(Datum, aes(x = `¿De donde provienen sus fondos?`)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, size = 8))
#ggsave("../Graphs/Funds.png")
```

```{r, echo=FALSE}
Datum %>%
  filter(`¿A que facultad pertenece?`!= "HUMA Programa de Estudios Interdisciplinarios, M.A. en Gestión y Administración Cultural")%>%
  filter(`¿De donde provienen sus fondos?`!= "Prestamo")%>%
  ggplot(aes(x = `¿Has tenido que incurrir en prestamos a pesar de tener un estipendio?`)) +
  geom_bar(na.rm = TRUE)
#ggsave("../Graphs/Loan.png")
```

```{r}
Datum %>%
  group_by(`Marca temporal`)%>%
  summarise(Gastos = sum(`¿Cuanto pagas en renta?`,`¿En promedio cuanto pagas en comida quincenalmente?`,`¿Cuanto paga en otros gastos recurentes?`)) %>%
  filter(Gastos!=is.na(Gastos)) %>%
  ggplot(aes(y = Gastos)) +
  geom_boxplot() +
  theme(axis.text.x = element_blank())+
  labs(y = "Dolares", title = "Gastos mensuales")

#ggsave("../Graphs/Gastos.png")
  
```

```{r}
ggplot(Datum, aes(y = `¿Cuantas horas trabaja semanales?`)) +
  geom_boxplot()+
  theme(axis.text.x = element_blank())+
  labs(y = "Horas", title = "Horas trabajadas semanales")

#ggsave("../Graphs/Workhours.png")
```



So that is the straight data, but what story does it tell?

## The story

```{r}
ggplot(Datum, aes(x = `Usted es ...`, fill = `¿De donde provienen sus fondos?`)) +
  geom_bar(position = "dodge") +
  theme(axis.text.x = element_text(size = 7)) +
  labs(y = "Numero de estudiantes", x = "", title = "Fuente de fondos por ciudadania")

#ggsave("../Graphs/FondosVnaional.png")

```

```{r}
Datum %>%
  filter(`¿A que facultad pertenece?`!= "HUMA Programa de Estudios Interdisciplinarios, M.A. en Gestión y Administración Cultural")%>%
  filter(`¿De donde provienen sus fondos?`!= "Prestamo")%>%
ggplot(aes(x = `¿Has tenido que incurrir en prestamos a pesar de tener un estipendio?`, fill = `¿De donde provienen sus fondos?`)) +
  geom_bar(position = "dodge") +
  labs(y = "Numero de estudiantes", x = "Necesitado prestamos", title = "Insidencia de Prestamo vs Fuente de ingresso")

#ggsave("../Graphs/PretamovsIngre.png")
```

```{r}
ggplot(Datum, aes(y = `¿Cuantas horas trabaja semanales?`, x = `¿De donde provienen sus fondos?`, fill = `¿De donde provienen sus fondos?`)) +
 geom_boxplot() +
  theme(axis.text.x = element_blank(), legend.text = element_text(size = 7))+
  labs(y = "Horas de trabajo semanales", x = "", title = "Horas de trabajo por fuente de fondos")

#ggsave("../Graphs/SourceVSwork.png")

```









